Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Model
Updated algorithm model figure.
Updated Model
Updatec Algorithm Model Image
Updated Paper
Population restart references updated.

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart). Population restart is the process in which we create a
    new set of individuals to replace the others that have already died (or
    were discarded) due to their aptitude. In a previous work
    \cite{Felix-Saul2022} we used to generate a new random set of solutions,
    with the cost of losing all evolution knowledge.

@@

    % If we are not going to add a State of the Art section, we need to mention other 
    % methods in the Introduction. - M
\section{Proposal}
    \label{section.proposal}

@@

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.
        % I do not like that image, is not very clear. We are confused by the 
        % similarity with Venn diagrams. Maybe is better to put boxes and arrows. - M

@@

        \begin{figure}
            \centering
            \includegraphics[width=80mm]{img/fig_algorithm_model.pdf}
            \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
            \end{figure}

>>>>

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart).

    Population restart is the process in which we create a
    new set of individuals to replace the others that have already died (or
    were discarded) due to their aptitude. In a previous work \cite{Felix-Saul2022} 
    we used to generate a new random set of solutions, with the cost of losing 
    all evolution knowledge. In the state of the art, we have found other methodologies 
    that have successfully sought to solve the problem of population extinction with
    restarts \cite{hellwig2020modified, loshchilov2013cma, jansen2010aging, tendresse2001effects, mathias1998effects}.

@@

\section{Proposal}
    \label{section.proposal}

@@

        Our algorithm's goal is to mimic the animal life cycle, where at any
        given moment, new individuals are born to be part of the population and
        participate in the collective evolution. As time passes, they grow
        older and mature, suffering changes throughout their lives that we
        chose to represent as mutations. In our analysis, we considered a
        couple's attraction a fundamental factor in reproduction. We thought of
        death's work to maintain balance in the population by enforcing the
        survival of the fittest. As in life, death can happen to everyone: from
        a newborn to the elderly, where fitness will determine the individual's
        longevity. We display the general model concept in
        Figure~\ref{fig.algorithm_model}.

@@

        \begin{figure}
            \centering
            \includegraphics[width=100mm]{img/fig_algorithm_model.pdf}
            \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
            \end{figure}
